Exploring the conformational dynamics of alanine dipeptide in solution subjected to an external electric field: A nonequilibrium molecular dynamics simulation

### 2014-03-05 writedown/npt-neq/reply/reply.tex
prepare the files for submission
convert for submission

Below you find our reply to the the referees. We apologize for the long time needed for the reply due to the holiday of one of the authors.  The request of the referees implied a rather massive additional computational effort. The result of such effort is highly satisfactory and the validity of the paper is now much higher. We are now confident that the paper can be accepted for publication.\\

@@

Yes, the CMAP correction is used. We mention it in the
section III.A. of the updated manuscript.
\\

@@

Yes, the definition of the probability fluxes is similar to the
kinetic rate (we use joint probabilities in (6) rather than
conditional probabilities).
However, we prefer to stick to our definition which
is mathematically simpler and univocal.
A comment along this direction has been added to the end of section III.B.
\\
% However, we want to stress out that, in general,
% the probability fluxes calculated in the manuscript should not be
% interpreted as a kinetic rate, and one cannot replace the
% non-equilibrium molecular dynamics by a kinetic analysis. The main
% reasons are:
% Firstly, for a non-equilibrium system, the probability fluxes are
% time-dependent, therefore, the lag-time $\Delta t$ in the definition (Eq.~(6))
% should be small compared with the typical time-scale of conformation change.\\
% Secondly, for a small lag time $\Delta t$ (1~ps in the manuscript), the conformational
% dynamics of biomolecules is generally not
% Markovian (see e.g.~C.~Sch\"utte et.~al.~JCP 2011 and J.-H.~Prinz et.~al.~JCP 2011).
% Since the basic assumption -- Markovianity -- of the kinetic analysis
% may not be satisfied, a direct
% application of the kinetic analysis in the non-equilibrium cases is questionable. Although one may
% gain useful information from the kinetic analysis, the reliability
% and the effectiveness of this approach should be carefully checked case
% by case.  Since the main goal of our research is to propose a
% non-equilibrium molecular dynamics simulation method, the numerical
% results are not compared with a kinetic analysis.\\

>>>>

Below you find our reply to the the referees. We apologize for the long time needed for the reply due to the holiday of one of the authors.
The request of the referees implied a rather massive additional computational effort.
The result of such effort is highly satisfactory and the validity of the paper is now much higher.
We are now confident that the paper can be accepted for publication.
To help the referees, we have also submitted a seperate file (alanine.pdf) with all changes to the manuscript colored in red.
\\

@@

Yes, the CMAP correction is used. We mention it in the
section III.A (3.1). of the updated manuscript.
\\

@@

Yes, the definition of the probability fluxes is similar to the
kinetic rate (we use joint probabilities in (6) rather than
conditional probabilities).
However, we prefer to stick to our definition which
is mathematically simpler and univocal.
A comment along this direction has been added to the end of section III.B (3.2).
\\
% However, we want to stress out that, in general,
% the probability fluxes calculated in the manuscript should not be
% interpreted as a kinetic rate, and one cannot replace the
% non-equilibrium molecular dynamics by a kinetic analysis. The main
% reasons are:
% Firstly, for a non-equilibrium system, the probability fluxes are
% time-dependent, therefore, the lag-time $\Delta t$ in the definition (Eq.~(6))
% should be small compared with the typical time-scale of conformation change.\\
% Secondly, for a small lag time $\Delta t$ (1~ps in the manuscript), the conformational
% dynamics of biomolecules is generally not
% Markovian (see e.g.~C.~Sch\"utte et.~al.~JCP 2011 and J.-H.~Prinz et.~al.~JCP 2011).
% Since the basic assumption -- Markovianity -- of the kinetic analysis
% may not be satisfied, a direct
% application of the kinetic analysis in the non-equilibrium cases is questionable. Although one may
% gain useful information from the kinetic analysis, the reliability
% and the effectiveness of this approach should be carefully checked case
% by case.  Since the main goal of our research is to propose a
% non-equilibrium molecular dynamics simulation method, the numerical
% results are not compared with a kinetic analysis.\\
